\documentclass[a4paper, 12pt]{article}

%\usepackage{savetrees}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{longtable}

%code for creating python code snippets
\usepackage{float}
\floatstyle{ruled}
\newfloat{python}{thp}{lop}
\floatname{python}{Listing}
%end code for creating python code snippets

\graphicspath{{./images/}}
\title {Student Robotics 2009\\ Assembly Guide}
\date{\today}
\setcounter{tocdepth}{1}


\begin{document}


\maketitle

\noindent This document explains how to connect up the Student Robotics electronics kit. It is a \textit{Getting Started Guide} and is not a comprehensive description of the hardware. For more information about individual boards, see the respective documentation, available from the website: http://www.srobo.org 

\section{Before You Begin}

Whilst some of the connecting cables are supplied to you, others will have to be put together yourself. Here is some general advice to follow when preparing your electronics kit:
\begin{itemize}
\item When assembling connectors you \textbf{must} follow the wiring guidelines as specified in the competition rules. This means using black wire for GND connections and red for 5V \& 12V. 
\item Keep wiring neat and securely terminated. Do not leave bare wires exposed. Keep connectors as short as possible.
\item \textbf{Never} make changes to your kit whilst it is switched on.
\item Mount \textbf{all} components securely using cable ties and the pcb standoffs supplied.

\end{itemize}


\section{Identify Kit Components}
Use the glossary in Section \ref{sec:glossary} to identify the different components. This will make the following stages easier.
\subsection{Types of Connector}
There are two types of connector used within the SR kit: 
\begin{itemize}
\item \textbf{RJ11 cables} - provide data connections (and small amount of power) to each of the boards, similar to USB cables. 
\item \textbf{SR Connectors} - supply power to some of the boards, the USB Hub and the battery.
\end{itemize} 

\input{power-assembly.tex}

\input{motor-assembly.tex}

\newpage
\input{pwm-assembly.tex}

\newpage
\input{jointio-assembly.tex}

\section{Conclusion}
Once you have tested each of the boards individually, you should write another python script to test all of the boards together. This will include testing the webcam. It is a very good idea to keep a copy of all of your test routines for use in the future when you make changes which inadvertently stop your robot working.

\newpage
\input{glossary}
\end {document}
